Combine_results

### 2017-04-10 Code/combine_results.Rmd
started lit review

```{r combine_results}
age_cod_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_", completed.states[1], ".csv"))
age_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_", completed.states[1], ".csv"))
BlackWhite_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_", completed.states[1], ".csv"))
cod_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_", completed.states[1], ".csv"))
cod_change_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_", completed.states[1], ".csv"))

mortality.rates <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_", completed.states[1], ".csv"))
mortality.rates.diff <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_diff_", completed.states[1], ".csv"))

@@

    age_cod_results <- rbind(age_cod_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_", completed.states[state_i], ".csv")))

    age_decomp_results <- rbind(age_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_", completed.states[state_i], ".csv")))

    BlackWhite_results <- rbind(BlackWhite_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_", completed.states[state_i], ".csv")))

    cod_decomp_results <- rbind(cod_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_marginal_", completed.states[state_i], ".csv")))

    cod_change_results <- rbind(cod_change_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_", completed.states[state_i], ".csv")))

  mortality.rates <- rbind(mortality.rates, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_", completed.states[state_i], ".csv")))

    mortality.rates.diff <- rbind(mortality.rates.diff, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_diff_", completed.states[state_i], ".csv")))
}

@@

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results_female, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results_female.csv")
write.csv(age_cod_results_male, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_cod_results_male.csv")
write.csv(age_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/age_decomp_results.csv")
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_decomp_results.csv")
write.csv(BlackWhite_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/BlackWhite_results.csv")
write.csv(cod_change_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/cod_change_results.csv")

write.csv(mortality.rates, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_combined.csv")
write.csv(mortality.rates.diff, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results/mortality_rates_diff_combined.csv")
```

>>>>

```{r combine_results_seed123}
age_cod_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_", completed.states[1], "_123.csv"))
age_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_decomp_", completed.states[1], "_123.csv"))
BlackWhite_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_", completed.states[1], "_123.csv"))
cod_decomp_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_marginal_", completed.states[1], "_123.csv"))
cod_change_results <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_change_", completed.states[1], "_123.csv"))

mortality.rates <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_", completed.states[1], "_123.csv"))
mortality.rates.diff <- read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_diff_", completed.states[1], "_123.csv"))

@@

    age_cod_results <- rbind(age_cod_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_", completed.states[state_i], "_123.csv")))

    age_decomp_results <- rbind(age_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_decomp_", completed.states[state_i], "_123.csv")))

    BlackWhite_results <- rbind(BlackWhite_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_", completed.states[state_i], "_123.csv")))

    cod_decomp_results <- rbind(cod_decomp_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_marginal_", completed.states[state_i], "_123.csv")))

    cod_change_results <- rbind(cod_change_results, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_change_", completed.states[state_i], "_123.csv")))

  mortality.rates <- rbind(mortality.rates, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_", completed.states[state_i], "_123.csv")))

    mortality.rates.diff <- rbind(mortality.rates.diff, read.csv(paste0("/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_diff_", completed.states[state_i], "_123.csv")))
}

@@

```{r save_combined_datasets, echo = F}
write.csv(age_cod_results_female, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_female.csv")
write.csv(age_cod_results_male, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_cod_results_male.csv")
write.csv(age_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/age_decomp_results.csv")
write.csv(cod_decomp_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_decomp_results.csv")
write.csv(BlackWhite_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/BlackWhite_results.csv")
write.csv(cod_change_results, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/cod_change_results.csv")

write.csv(mortality.rates, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_combined.csv")
write.csv(mortality.rates.diff, "/Users/corinneriddell/Documents/repos/BlackWhiteMortalityGap/Results2/mortality_rates_diff_combined.csv")
```
